### 2020-04-07 WorkSpace/Paper/conf_template.tex
added paper materials

% PACKAGES INCLUDED HERE 
% DO NOT NEED TO CHANGE
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

% AUTHOR NAMES AND TITLE GOES HERE
\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

% ABSTRACT AND KEYWORDS
\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

% SECTIONS
\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

% CREATES TABLE
\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

% CREATES IMAGE FIGURE
\begin{figure}[htbp]
\centerline{\includegraphics[width=\linewidth]{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\bibliographystyle{IEEEtran}
\bibliography{References}

\end{document}

### 2020-04-07 WorkSpace/ProjectCore/PRNGs.py
updated convnet architecture and data shaping. Still trying to resolve labeling issue, currently using outputwidth of 1 and categorical crossentropy as the loss. Error: Received a label value of -9223372036854775808 which is outside the valid range of [0, 1).

@@ -60,7 +60,6 @@ from numpy.random import Generator, MT19937, SeedSequence # For Merseene Twister
 </notes>
 '''
 def Middle_Square(seed, listlength):
-    print("Middle_Square")
     numlist = []
     for i in range(listlength):
         seedlength = len(str(seed))
@@ -105,7 +104,6 @@ def Middle_Square(seed, listlength):
 </notes>
 '''
 def Linear_Congruential(seed, listlength, modulus=4294967291, a=1588635695, c=1 ):
-    print("Linear_Congruential")
     numlist = []
     for i in range(listlength):
         seed = (a * seed + c) % modulus
@@ -130,7 +128,6 @@ def Linear_Congruential(seed, listlength, modulus=4294967291, a=1588635695, c=1 
 </notes>
 '''    
 def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
-    print("Lagged_Fibonacci")
     #litte dirty and expensive with validation checks
     #validation checks
     # 0 < j < k && k has to be greater than seed length.
@@ -138,7 +135,6 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
         return
     
     #If addition is used, it is required that at least one of the first k values chosen to initialise the generator be odd;
-    print("Lagged_Fibonacci")
     
     flag = False
     for i in range(k):
@@ -190,7 +186,6 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
 </notes>
 '''
 def Wichmann_Hill(seed1, seed2, seed3, listlength):
-    print("Wichmann_Hill")
     numlist = []
     for i in range(listlength):
        
@@ -238,7 +233,6 @@ def Wichmann_Hill(seed1, seed2, seed3, listlength):
 
 '''
 def Maximally_Periodic_Reciprocals(p, listlength, decprec=100):
-    print("Maximally_Periodic_Reciprocals")
     # In number theory, a prime number p is a Sophie Germain prime if 2p + 1 is also prime.
     
     #make whole
@@ -300,7 +294,6 @@ def Maximally_Periodic_Reciprocals(p, listlength, decprec=100):
 </notes>
 '''
 def Mersenne_Twister(seed, listlength):
-    print("Mersenne_Twister")
     numlist = []
     np.random.seed(seed)
     # numpy uses Mersenne Twister Algorithm
@@ -331,7 +324,6 @@ def Mersenne_Twister(seed, listlength):
 </notes>
 '''    
 def Park_Miller(seed, listlength):
-    
[…]

### 2020-04-10 WorkSpace/ProjectCore/Experiment.py
Created experiment class

@@ -1,0 +1,41 @@
+'''
+EXPERIMENTCONFIG = {
+    'SEED_METHOD' : ''  #using SEED_METHODS.py as source
+    'PRNG_METHOD' : '', #using PRNG_METHODS.py as source
+    'NUM_SETS' : '',    #generate NUM_SETS sets of length SET_LEN
+    'SET_LEN': '',
+    'IS_NEW_MODEL' : '',
+    'PATH' : '', #if IS_NEW_MODEL, new files will be created / overidden at this location. If !IS_NEW_MODEL, previous model with weights will be loaded. File must be named
+    'BATCH_SIZE': '',
+    'NUM_EPOCHS': '',
+    
+}
+'''
+
+
+
+
+
+from typing import Dict
+
+class Experiment:
+    def __init__(self, config : Dict):
+        
+        self.performcount = 0
+        
+        for key, value in d.items():
+            if value is None:
+                raise ValueError(key, ' must have a value associated')
+            if key == 'SEED_METHOD' || key == 'PRNG_METHOD' || key  == 'PATH':
+                if not isinstance(value, str):
+                    raise ValueError(key, ' must have a value type of str')
+            if key == 'NUM_SETS' || key == 'SETL_LEN' || key  == 'BATCH_SIZE' || key == 'NUM_EPOCHS':
+                if not isinstance(value, int):
+                    raise ValueError(key, ' must have a value type of int')
+            if key == 'IS_NEW_MODEL' && not isinstance(value, bool):
+                raise ValueError(key, ' must have a value type of bool')
+    
+
+    def perform(self):
+        self.performcount += 1
+        

### 2020-04-14 WorkSpace/ProjectCore/Core/PrngMethods.py
implemented lag_fab seed method

@@ -165,7 +165,7 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
             for i in range(len(seedlist)):
                 if i is 0:
                     val = int(seedlist[j-1]) + int(seedlist[k-1]) % 10 #arbitrary mod?
-                    numlist.append(out)
+                    numlist.append(val)
                 elif 0 < i < len(seedlist) - 1:
                     seedlist[i] = seedlist[i+1] # shift array
                 else:

### 2020-04-14 WorkSpace/ProjectCore/Core/SeedMethods.py

@@ -15,8 +15,8 @@ def ticks(t):
     #return (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds()
 
 
-
-    
+def ticks_LF(t):
+    return  int(str( int( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000 ))[-10:])
     
 
 

### 2020-04-15 WorkSpace/ProjectCore/Core/DataBroker.py
fixed lagged fibonacci stupid bugs

@@ -61,8 +61,11 @@ class DataBroker:
         for i in range(self.numsets):
             t = getattr(Core.SeedMethods, self.seed_method)(t)
             temp = getattr(Core.PrngMethods, self.prng_method)(t,self.setlength)
+            print(len(temp), 'and', self.setlength end = '<->')
+            print(t, end = ' ')
             for a in range(len(temp)): #little expensive
                 temp[a] = int(temp[a])
+            
             n = temp[-1]
             y.append(n)
             x.append(temp[:-1])

### 2020-04-15 WorkSpace/ProjectCore/Core/PrngMethods.py

@@ -139,16 +139,17 @@ def Linear_Congruential(seed, listlength, modulus=4294967291, a=1588635695, c=1 
 </notes>
 '''    
 def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
-    #litte dirty and expensive with validation checks
-    #validation checks
-    # 0 < j < k && k has to be greater than seed length.
-    if(not(0 < j and j < k) or len(str(seed)) < k ):
+    
+    # 0 < j < k
+    if(not(0 < j and j < k)):
         return
     
     #If addition is used, it is required that at least one of the first k values chosen to initialise the generator be odd;
-    
     flag = False
-    for i in range(k):
+    for i in range(len(str(seed))):
+        if(i > k):
+            flag = True
+            break
         if(int(str(seed)[i]) % 2 != 0):
             flag = True
             break

### 2020-04-15 WorkSpace/ProjectCore/Core/DataBroker.py
fixed recursion bug

@@ -61,8 +61,8 @@ class DataBroker:
         for i in range(self.numsets):
             t = getattr(Core.SeedMethods, self.seed_method)(t)
             temp = getattr(Core.PrngMethods, self.prng_method)(t,self.setlength)
-            print(len(temp), 'and', self.setlength end = '<->')
-            print(t, end = ' ')
+            #print(temp, 'and', self.setlength, end = '<->')
+            #print(t, end = ' ')
             for a in range(len(temp)): #little expensive
                 temp[a] = int(temp[a])
             

### 2020-04-15 WorkSpace/ProjectCore/Core/PrngMethods.py

@@ -150,6 +150,8 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
         if(i > k):
             flag = True
             break
+            
+        #print(str(seed)[i])
         if(int(str(seed)[i]) % 2 != 0):
             flag = True
             break

### 2020-04-15 WorkSpace/ProjectCore/Core/SeedMethods.py

@@ -16,7 +16,24 @@ def ticks(t):
 
 
 def ticks_LF(t):
-    return  int(str( int( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000 ))[-10:])
+    seed = int(str( int( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000 ))[-10:])
+    
+    flag = False
+    for i in range(len(str(seed))):
+        if(int(str(seed)[i]) % 2 == 0):
+            flag = False
+        else: # if digit is odd, we can break out of loop
+            flag = True
+            break;
+
+    if(flag):
+        #print(str(seed))
+        return seed
+    else:
+        seed = ticks_LF(t)
+        
+    return seed
+
     
 
 

### 2020-04-15 WorkSpace/ProjectCore/Core/Experiment.py
fixed graph label ... little long, might revise later

@@ -194,7 +194,7 @@ class Experiment:
         plt.plot(y_pred, color = 'blue', label = 'Predicted Data')
         plt.legend()
         plt.title('Correlation Plot From Testing\n')
-        plt.ylabel('Correlation')
+        plt.ylabel('Normalized PRN (Blue is Predicted ... Red is Target)')
         plt.xlabel('Sequential Prediction Index (from 0 to Num_SETs - 1)')
         
         y_pred = y_pred.flatten() #flatten y_pred to for PCC calculation to include in title

### 2020-04-15 WorkSpace/ProjectCore/Core/PrngMethods.py
Copied project proposal to root

@@ -144,19 +144,18 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
     if(not(0 < j and j < k)):
         return
     
-    #If addition is used, it is required that at least one of the first k values chosen to initialise the generator be odd;
+    #If addition is used, it is required that at least one of the first k values 
+    # chosen to initialise the generator be odd
     flag = False
     for i in range(len(str(seed))):
         if(i > k):
             flag = True
             break
             
-        #print(str(seed)[i])
         if(int(str(seed)[i]) % 2 != 0):
             flag = True
             break
     
-    #implementation  
     numlist = []
     seedlist = []
     
@@ -199,7 +198,11 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
         ... so I am assuming it can be over 30,000.
 </notes>
 '''
-def Wichmann_Hill(seed1, seed2, seed3, listlength):
+def Wichmann_Hill(seedlst, listlength):
+    seed1 = seedlst[0]
+    seed2 = seedlst[1]
+    seed3 = seedlst[2]
+    
     numlist = []
     for i in range(listlength):
        

### 2020-04-15 WorkSpace/ProjectCore/Core/SeedMethods.py

@@ -3,16 +3,23 @@ Normally, a (pseudo-)random number generator is a deterministic algorithm that g
 
 The seed for each PRNG will be the result of this.
 
-
 A single tick represents one hundred nanoseconds or one ten-millionth of a second. There are 10,000 ticks in a millisecond, or 10 million ticks in a second. This will allow enough spread between occaisonally retreived ticks, where we can assume reasonable pseudo-unpredictabililty. This serves as a simplistic and constantly changing control mechanism for being able to seed PRNGs and test experimental outcomes. While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).
+
+Note that t is an optional parameter if needed. Since the calls are genralized in DataBroker, parameters have to be the same.
 
 '''
 
 from datetime import *
+from time import sleep
 
 def ticks(t):
-    return int( str( int( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000 ))[-6:])
-    #return (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds()
+    
+    
+    #seed = int( str( int ( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000) )[-6:])
+    seed = (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds() * 10000000
+    print(seed, end = ' ')
+    return seed
+    #
 
 
 def ticks_LF(t):
@@ -27,7 +34,6 @@ def ticks_LF(t):
             break;
 
     if(flag):
-        #print(str(seed))
         return seed
     else:
         seed = ticks_LF(t)
@@ -35,6 +41,14 @@ def ticks_LF(t):
     return seed
 
     
-
-
+    
+def ticks_WH(t):
+    lst = []
+    for i in range(3):
+        lst.append(ticks(t))
+        #time delay
+        print(lst[i], end = ' ')
+        #print(lst[i],end = ' ')
+        sleep(1/lst[i])
+    return lst
 

### 2020-04-16 WorkSpace/ProjectCore/Core/Experiment.py
changes

@@ -189,6 +189,11 @@ class Experiment:
                   
         y_pred = self.pred.Predict(self.db.x_test, self.db.y_test)
         y_actual = self.db.y_test
+        
+        results = self.pred.model.evaluate(self.db.x_test, self.db.y_test, batch_size=15)
+    
+        print('test loss, test acc:', results)
+
 
         plt.plot(y_actual, color = 'red', label = 'Target Data')
         plt.plot(y_pred, color = 'blue', label = 'Predicted Data')
@@ -199,10 +204,10 @@ class Experiment:
         
         y_pred = y_pred.flatten() #flatten y_pred to for PCC calculation to include in title
 
-        #print(y_actual)
-        #print(y_pred)
-        #print(y_actual.shape)
-        #print(y_pred.shape)
+        #print('actual', y_actual)
+        #print('pred',y_pred)
+        print(y_actual.shape)
+        print(y_pred.shape)
 
         pearsoncorr = pearsonr(y_actual,y_pred)
         

### 2020-04-16 WorkSpace/ProjectCore/Core/PrngMethods.py

@@ -211,6 +211,7 @@ def Wichmann_Hill(seedlst, listlength):
         seed3 = 170 * seed3 % 30323
 
         numlist.append((float(seed1)/30269.0 + float(seed2)/30307.0 + float(seed3)/30323.0) % 1.0)
+    #print(numlist[0:50])
     return numlist
     
     

### 2020-04-16 WorkSpace/ProjectCore/Core/SeedMethods.py

@@ -13,13 +13,12 @@ from datetime import *
 from time import sleep
 
 def ticks(t):
-    
-    
-    #seed = int( str( int ( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000) )[-6:])
-    seed = (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds() * 10000000
-    print(seed, end = ' ')
-    return seed
-    #
+    t = int( str( int( (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds() * 10000000))[-6:])
+    if(t==0):
+        t = ticks()
+    return t
+        
+    #return (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds()
 
 
 def ticks_LF(t):
@@ -47,7 +46,7 @@ def ticks_WH(t):
     for i in range(3):
         lst.append(ticks(t))
         #time delay
-        print(lst[i], end = ' ')
+        #print(lst[i], end = ' ')
         #print(lst[i],end = ' ')
         sleep(1/lst[i])
     return lst

### 2020-04-16 WorkSpace/Paper/Paper.tex
paper additions

--- 2020-04-07 WorkSpace/Paper/conf_template.tex
@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+%\IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
@@
 
-% AUTHOR NAMES AND TITLE GOES HERE
-\title{Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+% TITLE GOES HERE
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
+\title{Predicting Pseudo Random Values Using Convolutional Neural Networks\\}
+
+% AUTHOR NAMES GOES HERE
+
+\author{
+\IEEEauthorblockN{Najib Ali}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
+email address}\\[0.2cm]  %<------- Extra vertical space
+\IEEEauthorblockN{Matthew Hawks}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
 email address}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
+\IEEEauthorblockN{Jacob Anderson}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
+email address}\\[0.2cm]  %<------- Extra vertical space
+\IEEEauthorblockN{Ryan Hines}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
 email address}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
+\IEEEauthorblockN{Spencer Arnold}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
+email address}\\[0.2cm]  %<------- Extra vertical space
+\IEEEauthorblockN{Tae Kweon}
+\IEEEauthorblockA{\textit{Department of Computer Science}\\
+\textit{Middle Tennessee State University}\\
+Murfreesboro, Tennessee \\
 email address}
@@
 
-% ABSTRACT AND KEYWORDS
+% ABSTRACT
+
 \begin{abstract}
@@
 
+% KEYWORDS
+
 \begin{IEEEkeywords}
@@
 
-% SECTIONS
+% INTRODUCTION SECTION
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
-\section{Ease of Use}
+Start typing here \cite{b1}.
 
-\subsection{Maintaining the Integrity of the Specifications}
+% BACKGROUND SECTION
+\section{Background}
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+Start typing here \cite{b2}.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+% METHODS SECTION
+\section{Methods}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+Start typing here \cite{b3}.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+% RESULTS SECTION
+\section{Results}
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+Start typing here \cite{b4}.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+% DISCUSSION SECTION
+\section{Discussion}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+Start typing here \cite{b5}.
 
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-% CREATES TABLE
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-% CREATES IMAGE FIGURE
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=\linewidth]{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
+% REFERENCES
+% THIS IS CREATED AUTOMATICALLY
 \bibliographystyle{IEEEtran}
-\bibliography{References}
+\bibliography{References} % change if another name is used for References file
 

### 2020-04-17 WorkSpace/ProjectCore/Core/Experiment.py
Cleaned code, logging, and re-ran tests.

@@ -90,8 +90,6 @@ class Experiment:
         self.performcount += 1
         loud_logging = self.config['LOUD_LOGGING']
         
-        
-        
         ### extra logging
         if(loud_logging):
             
@@ -149,8 +147,6 @@ class Experiment:
                                   disable_TQDMN = self.config['DISABLE_TQDMN']
                                   )
         
-        
-        
         if(loud_logging):
             print("Training Finished!\n\nPrinting results...\n")
             print("History Keys: ", history.history.keys())
@@ -158,9 +154,12 @@ class Experiment:
         
         ### summarize history for loss ###
         
-        # Note: if monitoring two metrics that are the same for checkpointing and training, you only need to display 'loss', which keras returns by default. 
-        # Otherwise if you want to see the metric associated with checkpoint monitor loss, you need to add that to the graph. Also note thatit might be advisable 
-        # to create two graphs for the latter, because different loss functions interpret loss differently, possibly not allowing you to see scaled plots correctly. 
+        # Note: if monitoring two metrics that are the same for checkpointing and training,
+        # you only need to display 'loss', which keras returns by default. 
+        # Otherwise if you want to see the metric associated with checkpoint monitor loss,
+        # you need to add that to the graph. Also note thatit might be advisable 
+        # to create two graphs for the latter, because different loss functions interpret
+        # loss differently, possibly not allowing you to see scaled plots correctly. 
         # you will have to add those accordingly. See print(history.history.keys())
         plt.plot(history.history['loss'], label = 'loss')
         plt.plot(history.history['val_loss'], label = 'validation_loss')
@@ -171,7 +170,8 @@ class Experiment:
         plt.ylabel('loss')
         plt.xlabel('epoch')
         #plt.legend(['loss', 'validation_loss',], loc='upper left') #'train_mae', 'test_mae'
-          
+        
+        #save loss plot
         i = 0
         while True:
             i += 1
@@ -183,36 +183,39 @@ class Experiment:
         
         plt.show()
         
-        
-                  
         ### summarize prediction data for regression analysis ###
-                  
+        
+        #predict (testing)
         y_pred = self.pred.Predict(self.db.x_test, self.db.y_test)
         y_actual = self.db.y_test
         
[…]

### 2020-04-17 WorkSpace/ProjectCore/Core/PredictiveModel.py

@@ -41,6 +41,8 @@ from scipy.stats.stats import pearsonr
 import os
 import shutil
 
+import pandas as pd
+
 class PredictiveModel:
     def __init__(self, input_width : int,  path:str, is_new_model=True, config='No Config Available'):
         self.path = path
@@ -95,7 +97,8 @@ class PredictiveModel:
         return model
 
     #Description:
-    #Trains the already created neural net with passed params for training and logging (using general file i/o, ModelCheckpoint, and CsvLogger).
+    #Trains the already created neural net with passed params for training and logging 
+    #(using general file i/o, ModelCheckpoint, and CsvLogger).
     #Note that Modelcheckpoint is always implemented, but parameters can be modified.
     def Train(self,
               x_train,
@@ -127,7 +130,6 @@ class PredictiveModel:
         """))
         
         
-        
         if(save_path == None):
             save_path = self.path
             
@@ -137,7 +139,12 @@ class PredictiveModel:
             
         #if(enable_checkpointing):
         #perhaps allow the user to enable model checkpointing in the future (with all params) and save the model at the bottom
-        checkpoint = ModelCheckpoint((save_path+'model.hd5'), monitor=monitor, verbose=verbose, save_weights_only=False, save_best_only=True, mode=mode)
+        checkpoint = ModelCheckpoint((save_path+'model.hd5'),
+                                     monitor=monitor,
+                                     verbose=verbose,
+                                     save_weights_only=False,
+                                     save_best_only=True,
+                                     mode=mode)
         
         csv_logger = CSVLogger((save_path+'training_log.csv'), append=append, separator=',')
         
@@ -148,17 +155,23 @@ class PredictiveModel:
         else:
             callbacks = [csv_logger, checkpoint, TQDMNotebookCallback()]
  
-        
         history = None
         if(use_validation):
-            #print('using validation split')
             #validation_data=validation_data is split between x and y
-            history = self.model.fit(x_train,y_train,batch_size=batch_size,epochs=epochs,validation_split=validation_split,verbose=verbose, callbacks=callbacks)
+            history = self.model.fit(x_train,
+                                     y_train,
+                                     batch_size=batch_size,
+                                     epochs=epochs,
+                                     validation_split=validation_split,
+                                     verbose=verbose,
+                                     callbacks=callbacks)
[…]

### 2020-04-17 WorkSpace/ProjectCore/Core/PrngMethods.py

@@ -1,47 +1,45 @@
 '''
+This file contains all of the PRNG methods used in this experiment.
 <notes>
-    Listed below are the PRNG implementations we want to focus on (this covers most of them from 1946-1998); however, 
-    we need to implement as many in this list as possible: https://en.wikipedia.org/wiki/List_of_random_number_generators
+    Listed below are the PRNG implementations we are focusing on (this covers a good amount of them from 1946-1998);
 
-      Done  [Middle-square method (1946)](https://en.wikipedia.org/wiki/Middle-square_method)
-      Done  [Lehmer generator / Park-Miller (1951)](https://en.wikipedia.org/wiki/Lehmer_random_number_generator)
-      Done  [Linear congruential generator (1958)](https://en.wikipedia.org/wiki/Linear_congruential_generator)
-      Done  [Lagged Fibonacci (1965)](https://en.wikipedia.org/wiki/Lagged_Fibonacci_generator)
-      Done  [Wichmann-Hill generator (1982)](https://en.wikipedia.org/wiki/Wichmann%E2%80%93Hill)
-      Done  [Maximally periodic reciprocals (1992)](https://en.wikipedia.org/wiki/Sophie_Germain_prime)
-      Done  [Mersenne Twister (1998)](https://en.wikipedia.org/wiki/Mersenne_Twister)
+        Done  [Middle-square method (1946)](https://en.wikipedia.org/wiki/Middle-square_method)
+        Done  [Linear congruential generator (1958)](https://en.wikipedia.org/wiki/Linear_congruential_generator)
+        Done  [Lagged Fibonacci (1965)](https://en.wikipedia.org/wiki/Lagged_Fibonacci_generator)
+        Done  [Mersenne Twister (1998)](https://en.wikipedia.org/wiki/Mersenne_Twister)
+        Done  [Park-Miller (1988)](https://en.wikipedia.org/wiki/Lehmer_random_number_generator)
+
+    Note that many of the notes in the below comments are mostly indirectly or directly referenced to the wiki pages. 
 
     The call definition of any given PRNG function should be as follows:
 
     PRNGfunc(seed, n, optionalparam=default, anotherparam=default). 
 
-    The function should return a list of n generated numbers using the generation method and all other params outside of seed and n need to have default values.
+    This is so we can experimentally automate the calling of each PRNG without getting too complex.
 
-    For example if I call PRNG(seed, 10)
[…]

### 2020-04-17 WorkSpace/ProjectCore/Core/SeedMethods.py

@@ -18,11 +18,10 @@ def ticks(t):
         t = ticks()
     return t
         
-    #return (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds()
-
-
 def ticks_LF(t):
-    seed = int(str( int( (datetime.utcnow() - datetime(1, 1, 1)).total_seconds() * 10000000 ))[-10:])
+    seed = int(str( int( (datetime.utcnow() - datetime(1970, 1, 1)).total_seconds() * 10000000 ))[-10:])
+    
+    len(str(seed))
     
     flag = False
     for i in range(len(str(seed))):
@@ -39,15 +38,5 @@ def ticks_LF(t):
         
     return seed
 
-    
-    
-def ticks_WH(t):
-    lst = []
-    for i in range(3):
-        lst.append(ticks(t))
-        #time delay
-        #print(lst[i], end = ' ')
-        #print(lst[i],end = ' ')
-        sleep(1/lst[i])
-    return lst
+
 

### 2020-04-20 WorkSpace/Paper/Paper.tex
Formatted results and added methods boilerplate in paper

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{listings}
+\usepackage{csquotes}
+\usepackage{float}
+\usepackage[caption=false]{subfig}
 \usepackage{cite}
@@
 Murfreesboro, Tennessee \\
-email address}\\[0.2cm]  %<------- Extra vertical space
+email address}\\[0.4cm]  %<------- Extra vertical space
 \IEEEauthorblockN{Matthew Hawks}
@@
 Murfreesboro, Tennessee \\
-email address}\\[0.2cm]  %<------- Extra vertical space
+email address}\\[0.4cm]  %<------- Extra vertical space
 \IEEEauthorblockN{Ryan Hines}
@@
 Murfreesboro, Tennessee \\
-email address}\\[0.2cm]  %<------- Extra vertical space
+email address}\\[0.4cm]  %<------- Extra vertical space
 \IEEEauthorblockN{Tae Kweon}
@@
 or Math in Paper Title or Abstract.
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+
 \end{abstract}
@@
 \section{Methods}
+\subsection{Seeding Method}
+We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed instead of gaining stochastic insight on the data from the PRNG.
+\newline
+The seed generation method we chose derives from the concept of using the system time as an element for seed generation.
+The specific implementation we chose took inspiration from Microsoft's .NET system.datetime.ticks property.
+[https://docs.microsoft.com/en-us/dotnet/api/system.datetime.ticks?view=netframework-4.8].
+We chose to single out this method due to its documentation and unqiue simplicity.
+System time is widely used as a parameter for modern seed generation methods.
+To put it more trivially: "a pseudo random number generator is a deterministic algorithm that, given an initial number (called seed), generates a sequence of numbers that adequately satisfies statistical randomness tests.
+Since the algorithm is deterministic, the algorithm will always generate the exact same sequence of numbers if it's initialized with the same seed.
+That's why system time (something that changes all the time) is usually used as the seed for random number generators." (https://stackoverflow.com/users/33708/mehrdad-afshari) \newline
+According to the Microsoft documentation, "A single tick represents one hundred nanoseconds or one ten-millionth of a second.
+There are 10,000 ticks in a millisecond, or 10 million ticks in a second.
+The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar."  \newline
+We used a fairly similar Python port 
+(https://stackoverflow.com/questions/29366914/what-is-python-equivalent-of-cs-system-datetime-ticks)
+\lstset{language=Python}
+\begin{lstlisting}[breaklines=true]
+def ticks(dt):
+    return (dt-datetime(1,1,1)).total_seconds()*10000000
+\end{lstlisting}
 
-Start typing here \cite{b3}.
+Porting side effects include:
+\begin{enumerate}
+    \item UTC times are assumed.
+    \item The resolution of the datetime object is given by datetime.resolution, which is datetime.timedelta(0, 0, 1) or microsecond resolution (1e-06 seconds).
+CSharp Ticks are purported to be 1e-07 seconds.
+\end{enumerate}
+
+Additional changes we made to our implementation:
+\begin{enumerate}
+    \item Changing start time from January 1, 0001 to January 1, 1970, which effectively reduced the length of the seed for experimental purposes.
+    \item Slicing last 6 digits of the ticks result to acquire more digit variation for frequent invocation.
+\end{enumerate}
+This final method allows enough spread between frequently retreived ticks, where we are assuming reasonable pseudo-unpredictabililty.
+This serves as a simplistic but constantly changing control mechanism for being able to seed PRNGs and test experimental outcomes.
+While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).\newline
+
+The original idea was to feed each PRNG different seeds from the same seed generator; however, many PRNG algorithms impose strict seed requirements to pass tests of randomness.
+Out of the five PRNG methods we implemented, Lagged Fibonacci was the only one that had special seed requirements, so we created a separate seed generator based on the same fundamental ticks generation method, but modified to meet the restrictions.
+Other PRNGs not implemented in this research that impose seed restrictions include Wichmann-Hill (which accepts three different seeds) and Maximally Periodic Reciprocals (which requires a Sophie Prime), among others.\newline
+
+You might ask: won't different seed generators introduce flaws or bias in the experiment?
+Well, it depends on what you are testing.
+In our case, we are strictly testing the "complexity" of the generator itself, so supplying a seed that is not blatantly predictable but also not unpredictable was sufficient.
+Our goal was to allow the charactaristics of the generator to be exposed, for we were cracking the "complexity" of the generation algorithm, not the complexity of an arbitrary seed.
 
@@
 
-Start typing here \cite{b4}.
+\begin{figure}[H]
+\centering
+\subfloat[Subfigure 1 list of figures text][Testing Regression Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Middle_Square_Reg.png}
+\label{fig:subfig1}}
+\qquad
+\subfloat[Subfigure 2 list of figures text][Training Loss Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Middle_Square_Loss.png}
+\label{fig:subfig2}}
+\caption{Middle Square Results}
+\label{fig:globfig}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfloat[Subfigure 1 list of figures text][Testing Regression Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Linear_Cong_Reg.png}
+\label{fig:subfig1}}
+\qquad
+\subfloat[Subfigure 2 list of figures text][Training Loss Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Linear_Cong_Loss.png}
+\label{fig:subfig2}}
+\caption{Linear Congruential Results}
+\label{fig:globfig}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfloat[Subfigure 1 list of figures text][Testing Regression Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Lagged_Fib_Reg.png}
+\label{fig:subfig1}}
+\qquad
+\subfloat[Subfigure 2 list of figures text][Training Loss Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Lagged_Fib_Loss.png}
+\label{fig:subfig2}}
+\caption{Lagged Fibonacci Results}
+\label{fig:globfig}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfloat[Subfigure 1 list of figures text][Testing Regression Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Park_Miller_Reg.png}
+\label{fig:subfig1}}
+\qquad
+\subfloat[Subfigure 2 list of figures text][Training Loss Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Park_Miller_Loss.png}
+\label{fig:subfig2}}
+\caption{Park Miller Results}
+\label{fig:globfig}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\subfloat[Subfigure 1 list of figures text][Testing Regression Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Twister_Reg.png}
+\label{fig:subfig1}}
+\qquad
+\subfloat[Subfigure 2 list of figures text][Training Loss Plot]{
+\includegraphics[width=0.4\linewidth]{./Images/Twister_Loss.png}
+\label{fig:subfig2}}
+\caption{Mersenne Twister Results}
+\label{fig:globfig}
+\end{figure}
 
@@
 \section{Discussion}
-
-Start typing here \cite{b5}.
-
-% REFERENCES
-% THIS IS CREATED AUTOMATICALLY
-\bibliographystyle{IEEEtran}
-\bibliography{References} % change if another name is used for References file
+Start typing here her is Start typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her is
 

### 2020-04-21 WorkSpace/Paper/Paper.tex
Expanded on method section, added appropriate references

@@
 \usepackage{textcomp}
+\usepackage{hyperref}
+\usepackage{url}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 The specific implementation we chose took inspiration from Microsoft's .NET system.datetime.ticks property.
-[https://docs.microsoft.com/en-us/dotnet/api/system.datetime.ticks?view=netframework-4.8].
-We chose to single out this method due to its documentation and unqiue simplicity.
+\cite{b1} We chose to single out this method due to its documentation and unqiue simplicity.
 System time is widely used as a parameter for modern seed generation methods.
@@
 Since the algorithm is deterministic, the algorithm will always generate the exact same sequence of numbers if it's initialized with the same seed.
-That's why system time (something that changes all the time) is usually used as the seed for random number generators." (https://stackoverflow.com/users/33708/mehrdad-afshari) \newline
+That's why system time (something that changes all the time) is usually used as the seed for random number generators." \cite{b2} \newline
 According to the Microsoft documentation, "A single tick represents one hundred nanoseconds or one ten-millionth of a second.
 There are 10,000 ticks in a millisecond, or 10 million ticks in a second.
-The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar."  \newline
-We used a fairly similar Python port 
-(https://stackoverflow.com/questions/29366914/what-is-python-equivalent-of-cs-system-datetime-ticks)
+The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar." \cite{b1}  \newline
+We used a fairly similar Python port, explained below. \cite{b3}
 \lstset{language=Python}
@@
 \end{enumerate}
+
 This final method allows enough spread between frequently retreived ticks, where we are assuming reasonable pseudo-unpredictabililty.
@@
 Our goal was to allow the charactaristics of the generator to be exposed, for we were cracking the "complexity" of the generation algorithm, not the complexity of an arbitrary seed.
+
+\subsection{PRNG Implementations}
+\subsection{Predictive Network}
+The predictor is a convolutional neural network implementing the function
+: $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/PredictiveModel.png}
+\caption{Predictive Model}
+\label{fig:globfig}
+\end{figure}
+
+\subsection{Experimental Setup}
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/ModelDiagram.png}
+\caption{Experiment Model}
+\label{fig:globfig}
+\end{figure}
 
@@
 
+.. code:: ipython3
+
+    % REFERENCES
+    % THIS IS CREATED AUTOMATICALLY
+    \bibliographystyle{IEEEtran}
+    \bibliography{References} % change if another name is used for References file
+
 \end{document}

### 2020-04-21 WorkSpace/Paper/Paper.tex
updated model and experiment graphs

@@
 \subsection{Predictive Network}
-The predictor is a convolutional neural network implementing the function
+NOTE THE Equation will have to be re-done and diagrams re-drawn to reflect our experiment.
+The predictor is a convolutional neural network implementing the function ...
 : $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
@@
 \centering
-\includegraphics[width=1\linewidth]{./Images/ModelDiagram.png}
+\includegraphics[width=1\linewidth]{./Images/SimpleModel.png}
+\caption{Experiment Model}
+\label{fig:globfig}
+\end{figure}
+
+\subsection{Experimental Setup}
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/GranularModel.png}
 \caption{Experiment Model}

### 2020-04-22 WorkSpace/Paper/Paper.tex
updated graphics for better clarity
Updated mathematical description of experiment and predictive model; also fixed figure and reference citations.

@@
 \usepackage{url}
+\usepackage{amsmath}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-Start typing here \cite{b1}.
-
 % BACKGROUND SECTION
 \section{Background}
-
-Start typing here \cite{b2}.
 
@@
 We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed instead of gaining stochastic insight on the data from the PRNG.
-\newline
+
 The seed generation method we chose derives from the concept of using the system time as an element for seed generation.
 The specific implementation we chose took inspiration from Microsoft's .NET system.datetime.ticks property.
-\cite{b1} We chose to single out this method due to its documentation and unqiue simplicity.
+\cite{msoftdocs} We chose to single out this method due to its documentation and unique simplicity.
 System time is widely used as a parameter for modern seed generation methods.
-To put it more trivially: "a pseudo random number generator is a deterministic algorithm that, given an initial number (called seed), generates a sequence of numbers that adequately satisfies statistical randomness tests.
+
+To put it more trivially: "a pseudo-random number generator is a deterministic algorithm that, given an initial number (called a seed), generates a sequence of numbers that adequately satisfy statistical randomness tests.
 Since the algorithm is deterministic, the algorithm will always generate the exact same sequence of numbers if it's initialized with the same seed.
-That's why system time (something that changes all the time) is usually used as the seed for random number generators." \cite{b2} \newline
+That's why system time (something that changes all the time) is usually used as the seed for random number generators." \cite{pseudoquote}
+
 According to the Microsoft documentation, "A single tick represents one hundred nanoseconds or one ten-millionth of a second.
 There are 10,000 ticks in a millisecond, or 10 million ticks in a second.
-The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar." \cite{b1}  \newline
-We used a fairly similar Python port, explained below. \cite{b3}
-\lstset{language=Python}
-\begin{lstlisting}[breaklines=true]
-def ticks(dt):
-    return (dt-datetime(1,1,1)).total_seconds()*10000000
-\end{lstlisting}
+The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar." \cite{msoftdocs}
 
-Porting side effects include:
+We used a fairly similar Python port, as seen in Figure ~\ref{fig:Default Seeding Method}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/Ticks.png}
+\caption{Default Seeding Method}
+\label{fig:Default Seeding Method}
+\end{figure}
+
+This python port of Microsoft's tick method can be attributed to "mhawke" on StackOverflow.
+\cite{tickport} The author had some noteworthy comments about this implementation, namely some porting side effects:
 \begin{enumerate}
     \item UTC times are assumed.
-    \item The resolution of the datetime object is given by datetime.resolution, which is datetime.timedelta(0, 0, 1) or microsecond resolution (1e-06 seconds).
+    \item The resolution of the DateTime object is given by DateTime.resolution, which is DateTime.timedelta(0, 0, 1) or microsecond resolution (1e-06 seconds).
 CSharp Ticks are purported to be 1e-07 seconds.
@@
 
-Additional changes we made to our implementation:
+For experimental needs, we made additional changes to the implementation:
 \begin{enumerate}
     \item Changing start time from January 1, 0001 to January 1, 1970, which effectively reduced the length of the seed for experimental purposes.
-    \item Slicing last 6 digits of the ticks result to acquire more digit variation for frequent invocation.
+    \item Slicing the last 6 digits of the ticks result to acquire more digit variation for frequent invocation.
 \end{enumerate}
 
-This final method allows enough spread between frequently retreived ticks, where we are assuming reasonable pseudo-unpredictabililty.
+The final modified method allows enough spread between frequently retrieved ticks, where we are assuming reasonable pseudo-unpredictability.
 This serves as a simplistic but constantly changing control mechanism for being able to seed PRNGs and test experimental outcomes.
-While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).\newline
+While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).
 
@@
 Out of the five PRNG methods we implemented, Lagged Fibonacci was the only one that had special seed requirements, so we created a separate seed generator based on the same fundamental ticks generation method, but modified to meet the restrictions.
-Other PRNGs not implemented in this research that impose seed restrictions include Wichmann-Hill (which accepts three different seeds) and Maximally Periodic Reciprocals (which requires a Sophie Prime), among others.\newline
+Other PRNGs not implemented in this research that impose seed restrictions include Wichmann-Hill (which accepts three different seeds) and Maximally Periodic Reciprocals (which requires a Sophie Prime), among others.
 
@@
 In our case, we are strictly testing the "complexity" of the generator itself, so supplying a seed that is not blatantly predictable but also not unpredictable was sufficient.
-Our goal was to allow the charactaristics of the generator to be exposed, for we were cracking the "complexity" of the generation algorithm, not the complexity of an arbitrary seed.
+Our goal was to allow the characteristics of the generator to be exposed, for we were cracking the "complexity" of the generation algorithm, not the complexity of an arbitrary seed.
 
 \subsection{PRNG Implementations}
-\subsection{Predictive Network}
-NOTE THE Equation will have to be re-done and diagrams re-drawn to reflect our experiment.
-The predictor is a convolutional neural network implementing the function ...
-: $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
+
+\subsection{Experimental Setup}
+
+The mathematical description of our experiment can be outlined below. 
+\begin{equation}
+\{0, G(S_n, k) \rightarrow \mathbb{L}_n \rightarrow Split(\mathbb{L}_n) \rightarrow \mathbb{X}_n,\mathbb{Y}_n , n \}
+\end{equation}
+Where the outer set builder notation iterates the following from 0 to n:
+Where $G$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector, $\mathbb{L}_n$, it is implied that $\mathbb{L}_n$ is the output vector of $G$ and $\mathbb{X}_n$ is $\mathbb{L}_n$ with the last element removed.
+$\mathbb{Y}_n$  is  used  as  the  corresponding  label for $\mathbb{X}_n$.
+
+The predictor is a convolutional neural network implementing the function...
+\begin{equation}
+P(\mathbb{X},\mathbb{Y}): \mathbb{X} \rightarrow \mathbb{B} \simeq \mathbb{Y}
+\end{equation}
+Where $\mathbb{X}_n$ represents a set containing $n$ sets of $k-1$ values generated from a PRNG where each $\mathbb{X}_n$ set is dervied from a different seed.
+$\mathbb{Y}_n$ represents a set containing $n$ sets of $kth$ values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \rightarrow \mathbb{Y}_n$.
+$P$, the predictive neural network, takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on the back-propagation due to previous predictions.
+
+For a simplified graphical representation of the latter description, please reference the predictive model in Figure ~\ref{fig:Predictive Model}, the simplified experimental model in Figure ~\ref{fig:Simplified Experimental Model} , and the granular view of the experimental model in Figure ~\ref{fig:Granular Experimental Model}.
+
 \begin{figure}[H]
@@
 \caption{Predictive Model}
-\label{fig:globfig}
+\label{fig:Predictive Model}
 \end{figure}
 
-\subsection{Experimental Setup}
 \begin{figure}[H]
@@
 \includegraphics[width=1\linewidth]{./Images/SimpleModel.png}
-\caption{Experiment Model}
-\label{fig:globfig}
+\caption{Simplified Experimental Model}
+\label{fig:Simplified Experimental Model}
 \end{figure}
 
-\subsection{Experimental Setup}
 \begin{figure}[H]
@@
 \includegraphics[width=1\linewidth]{./Images/GranularModel.png}
-\caption{Experiment Model}
-\label{fig:globfig}
+\caption{Granular Experimental Model}
+\label{fig:Granular Experimental Model}
 \end{figure}
@@
 \includegraphics[width=0.4\linewidth]{./Images/Middle_Square_Reg.png}
-\label{fig:subfig1}}
+\label{fig:MS_A}}
 \qquad
@@
 \includegraphics[width=0.4\linewidth]{./Images/Middle_Square_Loss.png}
-\label{fig:subfig2}}
+\label{fig:MS_B}}
 \caption{Middle Square Results}
-\label{fig:globfig}
+\label{fig:MS}
 \end{figure}
@@
 \includegraphics[width=0.4\linewidth]{./Images/Linear_Cong_Reg.png}
-\label{fig:subfig1}}
+\label{fig:LCG_A}}
 \qquad
@@
 \includegraphics[width=0.4\linewidth]{./Images/Linear_Cong_Loss.png}
-\label{fig:subfig2}}
+\label{fig:LCG_B}}
 \caption{Linear Congruential Results}
-\label{fig:globfig}
+\label{fig:LCG}
 \end{figure}
@@
 \includegraphics[width=0.4\linewidth]{./Images/Lagged_Fib_Reg.png}
-\label{fig:subfig1}}
+\label{fig:LF_A}}
 \qquad
@@
 \includegraphics[width=0.4\linewidth]{./Images/Lagged_Fib_Loss.png}
-\label{fig:subfig2}}
+\label{fig:LF_B}}
 \caption{Lagged Fibonacci Results}
-\label{fig:globfig}
+\label{fig:LF}
 \end{figure}
@@
 \includegraphics[width=0.4\linewidth]{./Images/Park_Miller_Reg.png}
-\label{fig:subfig1}}
+\label{fig:PM_A}}
 \qquad
@@
 \includegraphics[width=0.4\linewidth]{./Images/Park_Miller_Loss.png}
-\label{fig:subfig2}}
+\label{fig:PM_B}}
 \caption{Park Miller Results}
-\label{fig:globfig}
+\label{fig:PM}
 \end{figure}
@@
 \includegraphics[width=0.4\linewidth]{./Images/Twister_Reg.png}
-\label{fig:subfig1}}
+\label{fig:MT_A}}
 \qquad
@@
 \includegraphics[width=0.4\linewidth]{./Images/Twister_Loss.png}
-\label{fig:subfig2}}
+\label{fig:MT_B}}
 \caption{Mersenne Twister Results}
-\label{fig:globfig}
+\label{fig:MT}
 \end{figure}

### 2020-04-22 WorkSpace/Paper/Paper.tex
added boilerplate for PRNG descriptions and notes.

@@
 \subsection{PRNG Implementations}
+Middle Square:
+Description:
+...
+Notes:
+A note on weakness: For a generator of n-digit numbers, the period can be no longer than 8n. If the middle n digits are all zeroes, 
+the generator then outputs zeroes forever. If the first half of a number in the sequence is zeroes, the subsequent
+numbers will be decreasing to zero. While these runs of zero are easy to detect, they occur too frequently for this
+method to be of practical use. The middle-squared method can also get stuck on a number other than zero.
+
+An already seen list is NOT included in the original middle square method and will not be used.
+
+Linear Congruential:
+Description:
+...
+Notes:
+The generator is not sensitive to the choice of c, 
+as long as it is relatively prime to the modulus 
+(e.g. if m is a power of 2, then c must be odd), 
+so the value c=1 is commonly chosen.
+
+If c = 0, the generator is often called a multiplicative
+congruential generator (MCG), or Lehmer RNG. If c ≠ 0, the
+method is called a mixed congruential generator.
+
+Parameters were chosen based on $2^32$ in table 2 of 
+\url{https://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=BBA0C7ED3ADAB606642BB8D939774B4F?doi=10.1.1.34.1024&rep=rep1&type=pdf}
+
+Lagged Fibonacci:
+Description:
+...
+Notes:
+This is two tap, not three tap...
+It's a "lagged" generator, because "j" and "k" lag behind the generated pseudorandom value. 
+Also, this is called a "two-tap" generator, in that you are using 2 values in the sequence 
+to generate the pseudorandom number. However, a two-tap generator has some problems with 
+randomness tests, such as the Birthday Spacings. Apparently, creating a "three-tap" generator
+addresses this problem.
+
+Park Miller:
+Description:
+...
+Notes:
+The Lehmer generator is an lcg. Park Miller is a specific lcg.
+
+The Lehmer random number generator (named after D. H. Lehmer), 
+sometimes also referred to as the Park–Miller random number generator
+(after Stephen K. Park and Keith W. Miller), is a type of linear congruential generator (LCG).
+
+Park miller generator, because they essentially the same.
+Park-miller request the use of certain modulos.
+Lehmer is an lcg where c = 0...
+If c = 0, the generator is often called a multiplicative congruential generator (MCG),
+or Lehmer RNG. If c ≠ 0, the method is called a mixed congruential generator.
+
+While the Lehmer RNG can be viewed as a particular case of the linear congruential generator
+with c=0, it is a special case that implies certain restrictions and properties.
+In particular, for the Lehmer RNG, the initial seed must be coprime to the modulus m that is
+not required for LCGs in general.
+
+The choice of the modulus m and the multiplier a is also more restrictive for the Lehmer RNG.
+In contrast to LCG, the maximum period of the Lehmer RNG equals m−1 and it is such when m is 
+prime and a is a primitive root modulo m.
+
+Mersenne Twister:
+Description:
+...
+Notes:
+Closely related with LFSRs. In its MT19937 implementation is probably the most commonly used modern PRNG. 
+Default generator in the Python language starting from version 2.3.
+
+We used numpy's version of the Mersenne Twister.
 
@@
 \end{figure}
+
+\subsection{Experimental Execution}
 

### 2020-04-22 WorkSpace/ProjectCore/Core/PrngMethods.py
altered PRNG core code to reflect sequential ordering of PRNGs as invented for aesthetic reasons

@@ -6,8 +6,9 @@ This file contains all of the PRNG methods used in this experiment.
         Done  [Middle-square method (1946)](https://en.wikipedia.org/wiki/Middle-square_method)
         Done  [Linear congruential generator (1958)](https://en.wikipedia.org/wiki/Linear_congruential_generator)
         Done  [Lagged Fibonacci (1965)](https://en.wikipedia.org/wiki/Lagged_Fibonacci_generator)
-        Done  [Mersenne Twister (1998)](https://en.wikipedia.org/wiki/Mersenne_Twister)
         Done  [Park-Miller (1988)](https://en.wikipedia.org/wiki/Lehmer_random_number_generator)
+        Done  [Mersenne Twister (1998)](https://en.wikipedia.org/wiki/Mersenne_Twister)
+        
 
     Note that many of the notes in the below comments are mostly indirectly or directly referenced to the wiki pages. 
 
@@ -157,26 +158,6 @@ def Lagged_Fibonacci(seed, listlength, j=7 , k=10):
                     seedlist[i] = val
     return numlist
 
-
-'''
-<Mersenne_Twister finished=true/>
-<notes>
-    Closely related with LFSRs. In its MT19937 implementation is probably the most commonly used modern PRNG. 
-    Default generator in the Python language starting from version 2.3. 
-    
-    We used numpy's version of the Mersenne Twister.
-</notes>
-'''
-def Mersenne_Twister(seed, listlength):
-    numlist = []
-    np.random.seed(seed)
-    # numpy uses Mersenne Twister Algorithm
-    for i in range(listlength):
-        numlist.append(np.random.RandomState().randint(seed))
-        
-    return numlist
-    
-    
 '''
 <Park-Miller finished=true/>
 <notes>
@@ -214,6 +195,27 @@ def Park_Miller(seed, listlength):
         numlist.append(seed)
 
     return numlist
+
+'''
+<Mersenne_Twister finished=true/>
+<notes>
+    Closely related with LFSRs. In its MT19937 implementation is probably the most commonly used modern PRNG. 
+    Default generator in the Python language starting from version 2.3. 
+    
+    We used numpy's version of the Mersenne Twister.
+</notes>
+'''
+def Mersenne_Twister(seed, listlength):
+    numlist = []
+    np.random.seed(seed)
+    # numpy uses Mersenne Twister Algorithm
+    for i in range(listlength):
+        numlist.append(np.random.RandomState().randint(seed))
+        
+    return numlist
+    
+    
+
 
 
     

### 2020-04-23 WorkSpace/Paper/Paper.tex
updated notation and graphics

@@
 
-The mathematical description of our experiment can be outlined below. 
-\begin{equation}
-\{0, G(S_n, k) \rightarrow \mathbb{L}_n \rightarrow Split(\mathbb{L}_n) \rightarrow \mathbb{X}_n,\mathbb{Y}_n , n \}
-\end{equation}
-Where the outer set builder notation iterates the following from 0 to n:
-Where $G$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector, $\mathbb{L}_n$, it is implied that $\mathbb{L}_n$ is the output vector of $G$ and $\mathbb{X}_n$ is $\mathbb{L}_n$ with the last element removed.
-$\mathbb{Y}_n$  is  used  as  the  corresponding  label for $\mathbb{X}_n$.
+The following is a vastly informal mathematical representation of our experimental model, using a loose coupling of TLA+ notation and some set-builder theory.
+Further explanations and graphics will follow to aide in interpretation of the design of the experimental setup.
 
-The predictor is a convolutional neural network implementing the function...
-\begin{equation}
-P(\mathbb{X},\mathbb{Y}): \mathbb{X} \rightarrow \mathbb{B} \simeq \mathbb{Y}
-\end{equation}
-Where $\mathbb{X}_n$ represents a set containing $n$ sets of $k-1$ values generated from a PRNG where each $\mathbb{X}_n$ set is dervied from a different seed.
-$\mathbb{Y}_n$ represents a set containing $n$ sets of $kth$ values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \rightarrow \mathbb{Y}_n$.
-$P$, the predictive neural network, takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on the back-propagation due to previous predictions.
+Let $n$ be any arbitrary natural number such that $\{n \in \mathbb{N}\}$.
+Let $E$ represent the experiment definition.
+Let $seed$ be a function such that when called will return a seed.
+Given $k$ and $S_n$, let $prng$ be a function such that when called will return a set of pseudo random numbers,
+dervied from an initial seed $S_n$ and a given algorithm, where the length of the set is $k$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.5\linewidth]{./Images/ModelNotated.png}
+\caption{Notated Experiment Model}
+\label{fig:Notated Experiment Model}
+\end{figure}
+
+Given an enumerated set, $\mathbb{N}$:
+Where $prng$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$. 
+$\mathbb{X}_n$ represents a set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is dervied from a different seed.
+$\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$.
+$P$ a predictor function that represents a convolutional neural network, which takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on back-propagation due to previous predictions, thus using supervised learning to build a regression model.
 
@@
 \subsection{Experimental Execution}
+Highlight configuration parameters used to execute the experiment.
+Make a note the reasoning behind our small num of epochs and general reasoning behind all parameters.
 

### 2020-04-23 WorkSpace/Paper/Paper.tex
updated model and prng descriptions

@@
 \subsection{PRNG Implementations}
+For the experiment, we chose five PRNG methods by year of invention.
+We attempted to choose PRNG methods that displayed popularity in the world of pseudo random number generation while making sure the year of invention was reasonably distributed among the group.
+Choosing five PRNGs allowed us to focus on implementations, while leaving future research opportunities open for working with other PRNGs that we did not cover.
+
+Chosen PRNGs:
+\begin{itemize}
+  \item Middle-square method (1946)
+  \item Linear congruential generator (1958)
+  \item Lagged Fibonacci (1965)
+  \item Park-Miller (1988)
+  \item Mersenne Twister (1998)
+\end{itemize}
+
+The call definition of any given PRNG function is as follows:
+\begin{lstlisting}
+PRNGfunc(seed, n) 
+\end{lstlisting}
+This is so we can experimentally automate the calling of each PRNG without getting too complex.
+The given PRNG function should return a list of n generated numbers using the generation method.
+All other parameters outside of the seed and n are default values.
+
+For example, if the call was PRNG(seed, 10),
+it might return something like
+[3,5,10,1,31,17,2,4,6,7]
+
+We control parsing the n-length list and handling seeds externally. 
+This plays logically with separation of concerns for our usecase.
+
+While python generators can be useful iterating over previously generated iterables,
+we did not want to clutter our experimental execution code, so we stuck to a classical
+internal handling of all iterations.
+
+Below are short descriptions of each PRNG and any implementation notes made during the developement process.
 Middle Square:
@@
 
+\begin{displayquote}
 Let $n$ be any arbitrary natural number such that $\{n \in \mathbb{N}\}$.
@@
 dervied from an initial seed $S_n$ and a given algorithm, where the length of the set is $k$.
+\end{displayquote}
 
@@
 
-Given an enumerated set, $\mathbb{N}$:
-Where $prng$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$. 
-$\mathbb{X}_n$ represents a set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is dervied from a different seed.
+Given an enumerated set, $\mathbb{N}$,
+where $prng$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
+$\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is dervied from a different seed.
 $\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$.
@@
 For a simplified graphical representation of the latter description, please reference the predictive model in Figure ~\ref{fig:Predictive Model}, the simplified experimental model in Figure ~\ref{fig:Simplified Experimental Model} , and the granular view of the experimental model in Figure ~\ref{fig:Granular Experimental Model}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/SimpleModel.png}
+\caption{Simplified Experimental Model}
+\label{fig:Simplified Experimental Model}
+\end{figure}
+
+Referencing Figure ~\ref{fig:Simplified Experimental Model}, which is a visualization of what a 1-dimensional architecture of our experiment might entail, the predictive neural net as visualized in Figure ~\ref{fig:Predictive Model} is fed outputs of a specific PRNG, which will attempt to predict an kth value, based on previous k-1 values in a particular set of input data, where each set is generated based off of a single unique seed.
+After being trained on, ideally thousands of sets, the predictive network will form a better stochastic "understanding" of how the PRNG works underneath, thus being able to more accurately predict numbers generated from that PRNG in the future (i.e.,a supervised regression model).
+The backpropagation will flow through the predictive network to acheive the adversarial nature of a traditional GAN setup, but in reality, we won't be using a generative network, but rather a PRNG algorithm, so the generative part of our setup won't be defensive.
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\linewidth]{./Images/SimpleModel.png}
-\caption{Simplified Experimental Model}
-\label{fig:Simplified Experimental Model}
-\end{figure}
+Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively.
+The stack of convolutional layers allow the network to discover complex patterns in the input." [https://arxiv.org/pdf/1810.00378.pdf] Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus.
+Talk about the input xdata and ydata shape and reference the granular model Figure ~\ref{fig:Granular Experimental Model} for detail on how these data are aggregated.
 
@@
 \end{figure}
+
+Talk generally about the data aggregation process, just walk through it.
 

### 2020-04-24 WorkSpace/Paper/Paper.tex
finished most of methods, namely prng descriptions and fixed author formatting to correctly represent ranking as per the template

@@
 \author{
-\IEEEauthorblockN{Najib Ali}
+\IEEEauthorblockN{1\textsuperscript{st} Spencer Arnold}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 email address}\\[0.4cm]  %<------- Extra vertical space
-\IEEEauthorblockN{Matthew Hawks}
+\IEEEauthorblockN{4\textsuperscript{th} Matthew Hawks}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 \and
-\IEEEauthorblockN{Jacob Anderson}
+\IEEEauthorblockN{2\textsuperscript{nd} Najib Ali}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 email address}\\[0.4cm]  %<------- Extra vertical space
-\IEEEauthorblockN{Ryan Hines}
+\IEEEauthorblockN{5\textsuperscript{th} Ryan Hines}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 \and
-\IEEEauthorblockN{Spencer Arnold}
+\IEEEauthorblockN{3\textsuperscript{rd} Jacob Anderson}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 email address}\\[0.4cm]  %<------- Extra vertical space
-\IEEEauthorblockN{Tae Kweon}
+\IEEEauthorblockN{6\textsuperscript{th} Tae Kweon}
 \IEEEauthorblockA{\textit{Department of Computer Science}\\
@@
 
-Below are short descriptions of each PRNG and any implementation notes made during the developement process.
-Middle Square:
-Description:
-...
+Below are short descriptions and non-inclusive general notes of each PRNG and any implementation notes made during the developement process.
+
+\noindent\textbf{Middle Square}:
+\begin{itemize}
+    \item "To generate a sequence of n-digit pseudorandom numbers, an n-digit starting value is created and squared, producing a 2n-digit number.
+If the result has fewer than 2n digits, leading zeroes are added to compensate.
+The middle n digits of the result would be the next number in the sequence, and returned as the result.
+This process is then repeated to generate more numbers." \cite{MiddleSquare}
+\end{itemize}
 Notes:
-A note on weakness: For a generator of n-digit numbers, the period can be no longer than 8n. If the middle n digits are all zeroes, 
-the generator then outputs zeroes forever. If the first half of a number in the sequence is zeroes, the subsequent
-numbers will be decreasing to zero. While these runs of zero are easy to detect, they occur too frequently for this
-method to be of practical use. The middle-squared method can also get stuck on a number other than zero.
+\begin{itemize}
+    \item Generally the value of the seed has to be even, but can be padded with leading zeros.
+    \item If the middle n digits are all zeroes, the generator then outputs zeroes indefinitely.
+If the first half of a number in the sequence is zeroes, the subsequent numbers eventually converges to zero.
+\end{itemize}
 
-An already seen list is NOT included in the original middle square method and will not be used.
-
-Linear Congruential:
-Description:
-...
+\noindent\textbf{Linear Congruential}:
+\begin{itemize}
+    \item A linear congruential generator is a PRNG that represents an "additive  congruential  method", with foundations in improving upon "unsatisfactory" tests with entropy in fibonacci sequences.
+\cite{10.1145/321008.321019}
+\end{itemize}
 Notes:
-The generator is not sensitive to the choice of c, 
+\begin{itemize}
+    \item The generator is not sensitive to the choice of c, 
 as long as it is relatively prime to the modulus 
@@
 so the value c=1 is commonly chosen.
+    \item If c = 0, the generator is often called a multiplicative
+congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c ≠ 0, the
+method is called a mixed congruential generator.
+    \item Parameters were chosen based on $2^32$ numbers in table 2 of the article "Tables of linear congruential generators of different sizes and good lattice structure." \cite{LEcuyer1999TablesOL}
+\end{itemize}
 
-If c = 0, the generator is often called a multiplicative
-congruential generator (MCG), or Lehmer RNG. If c ≠ 0, the
-method is called a mixed congruential generator.
+\noindent\textbf{Lagged Fibonacci}:
+\begin{itemize}
+    \item The Lagged Fibonacci PRNG is a generalization of the Fibonacci Sequence \cite{lucas1891calcul}, where the sequence is generated based off a seed and the sum of the last two values is the PRN (which is also serves as the next seed).
+\end{itemize}
+Notes:
+\begin{itemize}
+    \item It is refered to a "lagged" generator, because "j" and "k" lag behind the generated pseudorandom value. 
+    \item Our implementation is called a "two-tap" generator, in that you are using 2 values in the sequence 
+to generate the pseudorandom number. However, note that a two-tap generator has some problems with 
+randomness tests, such as the Birthday Spacings. Creating a "three-tap" generator could
+addresses this problem.
+\end{itemize}
 
-Parameters were chosen based on $2^32$ in table 2 of 
-\url{https://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=BBA0C7ED3ADAB606642BB8D939774B4F?doi=10.1.1.34.1024&rep=rep1&type=pdf}
+\noindent\textbf{Park Miller}:
+\begin{itemize}
+    \item Park Miller (also known as Lehmer) can be viewed as a particular case of the Lemher PRNG, which is a particular case of the linear congruential PRNG, where c=0 and particular parameters are specified.
+\end{itemize}
+Notes:
+\begin{itemize}
+    \item "In 1988, Park and Miller \cite{10.1145/63039.63042}, suggested a Lehmer RNG with particular parameters m = 231 − 1 = 2,147,483,647 (a Mersenne prime M31) and a = 75 = 16,807 (a primitive root modulo M31), now known as MINSTD." \cite{ParkMiller}
+\end{itemize}
 
-Lagged Fibonacci:
-Description:
-...
+\noindent\textbf{Mersenne Twister}:
+\begin{itemize}
+    \item "The Mersenne Twister algorithm is based on a matrix linear recurrence over a finite binary field" \cite{10.1145/146382.146383}
+\end{itemize}
 Notes:
-This is two tap, not three tap...
-It's a "lagged" generator, because "j" and "k" lag behind the generated pseudorandom value. 
-Also, this is called a "two-tap" generator, in that you are using 2 values in the sequence 
-to generate the pseudorandom number. However, a two-tap generator has some problems with 
-randomness tests, such as the Birthday Spacings. Apparently, creating a "three-tap" generator
-addresses this problem.
-
-Park Miller:
-Description:
-...
-Notes:
-The Lehmer generator is an lcg. Park Miller is a specific lcg.
-
-The Lehmer random number generator (named after D. H. Lehmer), 
-sometimes also referred to as the Park–Miller random number generator
-(after Stephen K. Park and Keith W. Miller), is a type of linear congruential generator (LCG).
-
-Park miller generator, because they essentially the same.
-Park-miller request the use of certain modulos.
-Lehmer is an lcg where c = 0...
-If c = 0, the generator is often called a multiplicative congruential generator (MCG),
-or Lehmer RNG. If c ≠ 0, the method is called a mixed congruential generator.
-
-While the Lehmer RNG can be viewed as a particular case of the linear congruential generator
-with c=0, it is a special case that implies certain restrictions and properties.
-In particular, for the Lehmer RNG, the initial seed must be coprime to the modulus m that is
-not required for LCGs in general.
-
-The choice of the modulus m and the multiplier a is also more restrictive for the Lehmer RNG.
-In contrast to LCG, the maximum period of the Lehmer RNG equals m−1 and it is such when m is 
-prime and a is a primitive root modulo m.
-
-Mersenne Twister:
-Description:
-...
-Notes:
-Closely related with LFSRs. In its MT19937 implementation is probably the most commonly used modern PRNG. 
-Default generator in the Python language starting from version 2.3.
-
-We used numpy's version of the Mersenne Twister.
+\begin{itemize}
+    \item This PRNG is similar to a common LFSR. Its MT19937 implementation is probably the most commonly used modern PRNG. 
+    \item It is also the default generator in the Python language starting from version 2.3. 
+    \item For our implementation, we used numpy's version of the Mersenne Twister.
+\end{itemize}
 
@@
 Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively.
-The stack of convolutional layers allow the network to discover complex patterns in the input." [https://arxiv.org/pdf/1810.00378.pdf] Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus.
+The stack of convolutional layers allow the network to discover complex patterns in the input." \cite{debernardi2018pseudo} Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus.
 Talk about the input xdata and ydata shape and reference the granular model Figure ~\ref{fig:Granular Experimental Model} for detail on how these data are aggregated.

### 2020-04-25 WorkSpace/Paper/Paper.tex
added abstract, introduction, and discussion boilerplate. Also fixed some typos and formatting.

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Sample Abstract:
+OBJECTIVE: The role of antibiotic therapy in managing acute bacterial sinusitis (ABS) in children is controversial.
+The purpose of this study was to determine the effectiveness of high-dose amoxicillin/potassium clavulanate in the treatment of children diagnosed with ABS.
+
+METHODS: This was a randomized, double-blind, placebo-controlled study.
+Children 1 to 10 years of age with a clinical presentation compatible with ABS were eligible for participation.
+Patients were stratified according to age (<6 or ≥6 years) and clinical severity and randomly assigned to receive either amoxicillin (90 mg/kg) with potassium clavulanate (6.4 mg/kg) or placebo.
+A symptom survey was performed on days 0, 1, 2, 3, 5, 7, 10, 20, and 30.
+Patients were examined on day 14.
+Children’s conditions were rated as cured, improved, or failed according to scoring rules.
+
+RESULTS: Two thousand one hundred thirty-five children with respiratory complaints were screened for enrollment; 139 (6.5%) had ABS.
+Fifty-eight patients were enrolled, and 56 were randomly assigned.
+The mean age was 6630 months.
+Fifty (89%) patients presented with persistent symptoms, and 6 (11%) presented with nonpersistent symptoms.
+In 24 (43%) children, the illness was classified as mild, whereas in the remaining 32 (57%) children it was severe.
+Of the 28 children who received the antibiotic, 14 (50%) were cured, 4 (14%) were improved, 4(14%) experienced treatment failure, and 6 (21%) withdrew.
+Of the 28children who received placebo, 4 (14%) were cured, 5 (18%) improved, and 19 (68%) experienced treatment failure.
+Children receiving the antibiotic were more likely to be cured (50% vs 14%) and less likely to have treatment failure (14% vs 68%) than children receiving the placebo.
+
+CONCLUSIONS: ABS is a common complication of viral upper respiratory infections.
+Amoxicillin/potassium clavulanate results in significantly more cures and fewer failures than placebo, according to parental report of time to resolution.” (9)
 
@@
 \section{Introduction}
+Observation:
+
+Society relies on Pseudo-random numbers for a multitude of reasons.
+Whether the usecases fall in Information Security or, more broadly, modeling and simulation, we think it is important to not only push the boundary for the modern pseudo random number directly, but to also analyze the history of pseudo randomness to aide in that effort.
+
+Whether true randomness is a inhibition of the human perception or not, there is clear need to push the modern pseudo-random number closer to converging on perceived "true" randomness.
+
+Questions/Aim:
+
+To train a neural net to predict PRNs from a chosen PRNGs output.
+We aim to train neural nets to predict values of assigned PRNGs and track attributes of each to make generalized conclusions about the development of PRNGs with respect to time and any PRN correlations we uncover.
+
+Hypotheses:
+
+1) We predict there will be a positive trend over time on the cryptographic strength of each subsequent PRNG, given the nature of the increasing importance of stronger PRNGs.
+
+2) We also predict that as we get into cryptographically stronger generation methods, our prediction success rates (even with learning) will be less effective.
+
+3) We expect to uncover correlations in Pseudo-random numbers based on each individual generator, and aim to extract more generalized correlations between generators themselves.
 
@@
 Given an enumerated set, $\mathbb{N}$,
-where $prng$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
+where $prng$ is the chosen PRNG, $S_n$ is $n$th seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
 $\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is dervied from a different seed.
@@
 
-For a simplified graphical representation of the latter description, please reference the predictive model in Figure ~\ref{fig:Predictive Model}, the simplified experimental model in Figure ~\ref{fig:Simplified Experimental Model} , and the granular view of the experimental model in Figure ~\ref{fig:Granular Experimental Model}.
+For a simplified graphical representation of the latter description, please reference the predictive model in Figure~\ref{fig:Predictive Model}, the simplified experimental model in Figure~\ref{fig:Simplified Experimental Model} , and the granular view of the experimental model in Figure~\ref{fig:Granular Experimental Model}.
 
@@
 
-Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively.
+Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFF layers with 4 and 1 units, respectively.
 The stack of convolutional layers allow the network to discover complex patterns in the input." \cite{debernardi2018pseudo} Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus.
@@
 \section{Discussion}
-Start typing here her is Start typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her is
+
+Below are general notes for the discussion section....
+
+Mistakes Made / how the research could be made more robust.
+
+uncertainties
+
+Practical Application:
+A GAN method similar to this could be used in the future during a real-time prediction attack scenario.
+If attackers are somehow able to break a strong PRNG that is used to generate numbers for cryptographic methods, a method like this could be used as a defense mechanism to prevent (or slow down) further PRN generation cycles from being compromised.
+
+This provides a better framework for implementing new PRNGs, seed methods, and experimental designs... and fixing ours to be more mathematically accurate or more robust.
+
+With the results we obtained by doing mere 20 epochs, a lot heavier training and testing could be implemented with powerful computation power.
+
+The base code, such as seeding and PRNG code can also be significantly improved upon to be more mathematically accurate and produce better training and testing of models...
 

### 2020-04-28 WorkSpace/Paper/Paper.tex
pre-final draft and milestone

--- 2020-04-24 WorkSpace/Paper/Paper.tex
@@
 
+\IEEEspecialpapernotice{\\Middle Tennessee State University\\1301 East Main Street
+Murfreesboro, TN 37132-0001\\Department of Computer Science\\~\\}
+
 % AUTHOR NAMES GOES HERE
-
 \author{
 \IEEEauthorblockN{1\textsuperscript{st} Spencer Arnold}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}\\[0.4cm]  %<------- Extra vertical space
+sra4d@mtmail.mtsu.edu \\
+sa.education@outlook.com\\[0.4cm]  %<------- Extra vertical space
 \IEEEauthorblockN{4\textsuperscript{th} Matthew Hawks}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}
+mdh7r@mtmail.mtsu.edu \\
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Najib Ali}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}\\[0.4cm]  %<------- Extra vertical space
+\IEEEauthorblockN{2\textsuperscript{nd} Abdinajib Ali}
+aaa2ak@mtmail.mtsu.edu\\
+hanut.ali96@gmail.com\\[0.4cm]  %<------- Extra vertical space
 \IEEEauthorblockN{5\textsuperscript{th} Ryan Hines}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}
+rch5b@mtmail.mtsu.edu \\
 \and
 \IEEEauthorblockN{3\textsuperscript{rd} Jacob Anderson}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}\\[0.4cm]  %<------- Extra vertical space
+jaa5v@mtmail.mtsu.edu\\[0.8cm]  %<------- Extra vertical space
 \IEEEauthorblockN{6\textsuperscript{th} Tae Kweon}
-\IEEEauthorblockA{\textit{Department of Computer Science}\\
-\textit{Middle Tennessee State University}\\
-Murfreesboro, Tennessee \\
-email address}
+thk2e@mtmail.mtsu.edu \\
 }
-
 \maketitle
@@
 % ABSTRACT 
-
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-
+Pseudo-Random number generators (PRNG) are a cornerstone if not the foundation for cryptography.
+The quality of generated pseudo-random numbers (PRN) can usually determine the "cryptographic strength" of a given system.
+As history shows us, there have been numerous attempts to create PRNGs that decrease the general predictability and correlation of each subsequent value produced.
+We introduce a novel approach to predicting sequences of given PRNGs by proposing the use of deep convolutional networks (CNN) in a regression-based supervised learning process.
+We also provide an experimental framework for the latter and, in addition to building off of existing prediction models, we demonstrate that the cryptographic strength of each consecutive PRNG increases, while prediction success rates (even with learning) are generally less effective.
+At the core, this is based upon the nature of the increasing importance of stronger PRNGs across industries.
 \end{abstract}
@@
 % KEYWORDS
-
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+pseudo random number (PRN), pseudo random number generator (PRNG), convolutional neural networks (CNN), neural cryptography.
 \end{IEEEkeywords}
@@
 \section{Introduction}
+Society relies on Pseudo-random numbers for a multitude of reasons.
+Whether the use cases fall in Information Security or, more broadly, modeling and simulation, we think it is important to not only push the boundary for the modern pseudo-random number directly but to also analyze the history of pseudo randomness to aide in that effort.
+Whether true randomness is an inhibition of the human perception or not, there is a clear need to push the modern pseudo-random number closer to converging on perceived "true" randomness.
+Our main aim was to train a predictive neural net to predict the values of different PRNGs and come to generalized conclusions about the development of PRNGs with respect to time, in addition to any PRN correlations we uncover.
+
+We approached this goal by implementing five PRNGs:
+\begin{itemize}
+  \item Middle-square method (1946)
+  \item Linear congruential generator (1958)
+  \item Lagged Fibonacci (1965)
+  \item Park-Miller (1988)
+  \item Mersenne Twister (1998)
+\end{itemize}
+
+These PRNGs will be looked at in depth in the methods section, but we mainly chose these five because they represent key points of progression in the developement of stronger PRNGs chronologically.
+Although five were chosen, the door is open to test other PRNGs in future research.
+
+Before conducting the research, we formed the following hypotheses:
+\begin{enumerate}
+    \item We predict there will be a positive trend over time on the cryptographic strength of each subsequent PRNG, given the nature of the increasing importance of stronger PRNGs.
+    \item We also predict that, as we get into cryptographically stronger generation methods, our prediction success rates (even with learning) will be less effective.
+    \item We expect to uncover correlations in PRNs based on each individual generator and aim to extract more generalized correlations between generators themselves.
+\end{enumerate}
 
@@
 \section{Background}
+PRNGs are generally deterministic algorithms that take in an input seed to generate PRNs that may or may not be tractable using statistical means.
+In this research, we use convolutional neural networks to try to predict the next set of random numbers generated from a PRNG.
+Typically, convolutional neural nets (CNNs) are used to tackle image classification problems; however, their design, stemming from the architecture of an underlying multi-layer perceptron, allows localized pattern detection that is extremely powerful in gaining insight from potentially noisy data, as in common cases of signal processing.\cite{Markell94}
+"CNNs exploit spatial locality by enforcing a local connectivity pattern between neurons of adjacent layers.
+The architecture thus ensures that the learned "filters" produce the strongest response to a spatially local input pattern." \cite{CNN}
+This is useful in problems where sequential analysis (like in time series problems) is prevalent.
+Oftentimes, CNNs are viewed as introductory ways of image classification without many other applications.
+When thinking of pixel data as an enumerated sequence of numbers, one can start to uncover the application of CNNs in other areas, like building a regression model for sequences of pseudo-random number data.
+In the following sections, we will discuss just that.
 
@@
 \subsection{Seeding Method}
-We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed instead of gaining stochastic insight on the data from the PRNG.
+We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed, instead of gaining stochastic insight on the data from the PRNG.
 
@@
 \cite{msoftdocs} We chose to single out this method due to its documentation and unique simplicity.
-System time is widely used as a parameter for modern seed generation methods.
+In general, system time is widely used as a parameter for modern seed generation methods.
 
@@
 The original idea was to feed each PRNG different seeds from the same seed generator; however, many PRNG algorithms impose strict seed requirements to pass tests of randomness.
-Out of the five PRNG methods we implemented, Lagged Fibonacci was the only one that had special seed requirements, so we created a separate seed generator based on the same fundamental ticks generation method, but modified to meet the restrictions.
+Out of the five PRNG methods we implemented, Lagged Fibonacci was the only one that had special seed requirements, so we created a separate seed generator based on the same fundamental ticks generation method, but modified it to meet the restrictions.
 Other PRNGs not implemented in this research that impose seed restrictions include Wichmann-Hill (which accepts three different seeds) and Maximally Periodic Reciprocals (which requires a Sophie Prime), among others.
@@
 \subsection{PRNG Implementations}
-For the experiment, we chose five PRNG methods by year of invention.
-We attempted to choose PRNG methods that displayed popularity in the world of pseudo random number generation while making sure the year of invention was reasonably distributed among the group.
-Choosing five PRNGs allowed us to focus on implementations, while leaving future research opportunities open for working with other PRNGs that we did not cover.
-
-Chosen PRNGs:
-\begin{itemize}
-  \item Middle-square method (1946)
-  \item Linear congruential generator (1958)
-  \item Lagged Fibonacci (1965)
-  \item Park-Miller (1988)
-  \item Mersenne Twister (1998)
-\end{itemize}
+As outlined in the introduction, we chose five PRNG methods by year of invention.
+Choosing five PRNGs allowed us to focus on implementations, while leaving future research opportunities open for others we did not cover.
+This sub-section highlights descriptions of the experimental role PRNGs played in our research and descriptions/notes we made about each PRNG implementation we created.
 
@@
 \end{lstlisting}
+
 This is so we can experimentally automate the calling of each PRNG without getting too complex.
@@
 The following is a vastly informal mathematical representation of our experimental model, using a loose coupling of TLA+ notation and some set-builder theory.
-Further explanations and graphics will follow to aide in interpretation of the design of the experimental setup.
+Further explanations and graphics will follow to aid in the interpretation of the design of the experimental setup.
 
@@
 Given an enumerated set, $\mathbb{N}$,
-where $prng$ is the chosen PRNG, $S_n$ is nth seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
-$\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is dervied from a different seed.
+where $prng$ is the chosen PRNG, $S_n$ is $n$th seed in the iteration, and $k$ is the length of the desired output vector ($\mathbb{L}_n$) of $prng$,
+$\mathbb{X}_n$ represents an enumerated set containing $n$ sets of $k-1$ values generated from a PRNG ($prng$) and each $\mathbb{X}_n$ set is derived from a different seed.
 $\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$.
@@
 
-For a simplified graphical representation of the latter description, please reference the predictive model in Figure ~\ref{fig:Predictive Model}, the simplified experimental model in Figure ~\ref{fig:Simplified Experimental Model} , and the granular view of the experimental model in Figure ~\ref{fig:Granular Experimental Model}.
+For a simplified graphical representation of the latter description, please reference the predictive model in Figure~\ref{fig:Predictive Model}, the simplified experimental model in Figure~\ref{fig:Simplified Experimental Model}, and the granular view of the experimental model in Figure~\ref{fig:Granular Experimental Model}.
 
@@
 
-Referencing Figure ~\ref{fig:Simplified Experimental Model}, which is a visualization of what a 1-dimensional architecture of our experiment might entail, the predictive neural net as visualized in Figure ~\ref{fig:Predictive Model} is fed outputs of a specific PRNG, which will attempt to predict an kth value, based on previous k-1 values in a particular set of input data, where each set is generated based off of a single unique seed.
-After being trained on, ideally thousands of sets, the predictive network will form a better stochastic "understanding" of how the PRNG works underneath, thus being able to more accurately predict numbers generated from that PRNG in the future (i.e.,a supervised regression model).
-The backpropagation will flow through the predictive network to acheive the adversarial nature of a traditional GAN setup, but in reality, we won't be using a generative network, but rather a PRNG algorithm, so the generative part of our setup won't be defensive.
+Referencing Figure~\ref{fig:Simplified Experimental Model}, which is a visualization of what a 1-dimensional architecture of our experiment might entail, the predictive neural net as visualized in Figure~\ref{fig:Predictive Model} is fed outputs of a specific PRNG, which will attempt to predict a kth value, based on previous k-1 values in a particular set of input data, where each set is generated based off of a single unique seed.
+After being trained on, ideally thousands of sets, the predictive network will form a better stochastic "understanding" of how the PRNG works underneath, thus being able to more accurately predict numbers generated from that PRNG in the future (i.e., a supervised regression model).
+The backpropagation will flow through the predictive network to achieve the adversarial nature of a traditional GAN setup, but in reality, we won't be using a generative network, but rather a PRNG algorithm, so the generative part of our setup won't be defensive.
 
@@
 
-Referencing Figure ~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max pooling layer and two FCFFlayers with 4 and 1 units, respectively.
-The stack of convolutional layers allow the network to discover complex patterns in the input." \cite{debernardi2018pseudo} Explain here how/why we used that research's dicriminator model in our experiment exactly, except we implemented Relus instead of leaky-relus.
-Talk about the input xdata and ydata shape and reference the granular model Figure ~\ref{fig:Granular Experimental Model} for detail on how these data are aggregated.
+Referencing Figure~\ref{fig:Predictive Model}, which is a visualization of the layer stack we used for the predictive network in each trial of the experiment, it "consists of four stacked convolutional layers, each with 4 filters, kernel size 2, and stride 1, followed by a max-pooling layer and two FCFF layers with 4 and 1 units, respectively.
+The stack of convolutional layers allow the network to discover complex patterns in the input." \cite{debernardi2018pseudo} We used the existing design of research in a similar area at the aforementioned quote.
+We were able to adapt their discriminative model to fit the needs of our predictive model.
+The main difference in our model is that we implemented Relus instead of leaky-relus.
+The meaning of our input and output was also inherently different.
+View the granular model Figure~\ref{fig:Granular Experimental Model} for more detail on how the input data sets were generated.
 
@@
 
-Talk generally about the data aggregation process, just walk through it.
+Referencing Figure~\ref{fig:Granular Experimental Model}, which is a granular visualization of our experiment, representing the multi-dimensionality in the generation and aggregation of our data.
+Note that this is the same general process as illustrated in Figure~\ref{fig:Predictive Model}.
+The splitting occurs with the data set that is output from the PRNG, which is of k-length, where k-1 values and kth values get split into separate vectors.
+Note that the data generation and aggregation process is repeated twice: once to produce the training data and once to produce the testing data.
+Given the fact that we are using PRNs as our training and testing data, this allows us the flexibility to generate thousands of data sets, whereas in most problems concerning neural networks, training and testing data sets are pre-validated and oftentimes this data is limited.
+Given the circumstance, we could generate an arbitrary amount of training and testing data, given that our PRNG implementation is mathematically sound and algorithmically robust.
 
 \subsection{Experimental Execution}
-Highlight configuration parameters used to execute the experiment.
-Make a note the reasoning behind our small num of epochs and general reasoning behind all parameters.
+For the execution of the experiment, we invoked an experimental process and predictive model as described in the last section.
+We then loaded each PRNG individually and executed the experiment with the following parameters for training:
+\begin{itemize}
+\item Number of sets: 1000
+\item Length of each set (where each set gets a new seed): 2000
+\item batch size: 15
+\item Number of epochs: 30
+\item Validation split: 0.3
+\item Optimization method: nadam
+\item Learning rate: 0.001
+\item Loss method: mean absolute error
+\end{itemize}
+
+After training, we had five separate trained prediction models corresponding to each PRNG.
+We then tested our models with the testing data and produced correlation coefficients to track how well our models represented new test data from each PRNG.
 
@@
 \section{Results}
-
+The following are the regression and loss plots resulting from the testing of each predictive model.
 \begin{figure}[H]
@@
 \end{figure}
+
+Referencing Figure~\ref{fig:MS}, our predictive model did quite well; representing about 90% of the variability in the data from the middle square PRNG.
 
@@
 
+Referencing Figure~\ref{fig:LCG}, our predictive model did not do well; representing about 3.5% of the variability in the data from the linear congruential PRNG.
+Note that with a 2-tailed p-value of 0.26, there is an indication of weak evidence for a strong model, so we can not be conclusive.
+We believe that increasing the quantity of training data would aide in making this a stronger model with a higher correlation coefficient and lower p-value, in addition to more training time.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+Referencing Figure~\ref{fig:LF}, our predictive model did not do well; representing about 49% of the variability in the data from the lagged fibonacci PRNG.
+Note that with a 2-tailed p-value of 6.4 (which is significantly worse than linear congruential), there is an indication of weak evidence for a strong model, so we can not be conclusive.
+We believe that increasing the quantity of training data would aide in making this a stronger model with a higher correlation coefficient and lower p-value, in addition to more training time.
 
@@
 
+Referencing Figure~\ref{fig:PM}, our predictive model did not do well; representing about 3.6% of the variability in the data from the Park Miller PRNG.
+Note that with a 2-tailed p-value of 0.25, there is an indication of weak evidence for a strong model, so we can not be conclusive.
+We believe that increasing the quantity of training data would aide in making this a stronger model with a higher correlation coefficient and lower p-value, in addition to more training time.
+
 \begin{figure}[H]
@@
 
+Referencing Figure~\ref{fig:MT}, our predictive model did not do well; representing about 1.4% of the variability in the data from the Mersenne Twister PRNG.
+Note that with a 2-tailed p-value of 0.65, there is an indication of weak evidence for a strong model, so we can not be conclusive.
+We believe that increasing the quantity of training data would aide in making this a stronger model with a higher correlation coefficient and lower p-value, in addition to more training time.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{./Images/cotrend.png}
+\caption{Correlation Trend}
+\label{fig:Correlation Trend}
+\end{figure}
+As you can see in Figure~\ref{fig:Correlation Trend}, we noticed a generally positive trend over time on the cryptographic strength of each subsequent PRNG (represented by the negative trend of the "successfulness" of each predictive model).
+We also can demonstrate that as we get into cryptographically stronger generation methods, our prediction success rates are noticeably less effective.
+Although we didn't necessarily uncover specific correlations surrounding PRNs themselves, we were able to lightly train models that, given more robust training parameters, show promise in converging a model to predict values with weak seeds.
+Our models also show promise due to the general progression of our loss plots, showing improvement with virtually every epoch.
+
 % DISCUSSION SECTION
 \section{Discussion}
-Start typing here her is Start typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her isStart typing here her is
+Our main aim was to train a predictive neural net to predict the values of different PRNGs and come to generalized conclusions about the development of PRNGs with respect to time.
+Throughout this research, we also ran into minor problems and noticed possible errors we could have made.
+Given the highly statistically precise nature of PRN generation in general, there are also areas that we could have improved on to reduce that experimental margin of error.
+
+While developing the PRNG implementations we were having problems with the seed generation in general and recognize that a more robust seeding method could be created to eliminate the possibility for the seed to "converge" to 0.
+We also realize this could be a bug in the experimental code, but served nothing more than an inconvenience in the execution of the experiment.
+On occasion, we also experienced convergence to zero while using the middle-square PRNG implementation.
+On occasion the middle square implementation will converge to 0 and will cause the network training to train on convergent data, leading to faulty results when testing the predictive network.
+This in large has to do with the Middle-Square algorithm being known to converge given certain numbers.
+
+Other than slight ambiguity in errors, we realize that our PRNG methods might not be perfect implementations.
+Some generators have tight tolerances for parameters and algorithmic behaviors.
+While we believe that our implementations are sound, they could be checked and improved upon by using tests of statistical randomnesses, such as the National Institute of Standards and Technology (NIST) provides.
+Different seeding methods could also provide different results, given that our seeding method was relatively linear and weak in design.
+
+Through working on this research, we also developed an architecture that could be reused by other researchers in the future for experimentation on improved seeding methods and improved generation methods.
+In addition, we only ran the experiment for 30 epochs, so more computational time could be used to improve our results.
+
+In terms of application, some practical applications for this model could be used in the future during a real-time prediction attack.
+If attackers were somehow able to break a strong PRNG that is used for cryptographic methods, a method like this could be used to prevent or slow down further PRN generation cycles from being compromised.
+
+Lastly, We encourage further work on improving the seeding methods, PRNG methods, training parameters, and model selection to produce more mathematically accurate and robust results.
 

### 2020-04-29 WorkSpace/Paper/Paper.tex
fixed paper typos

@@
     \item If c = 0, the generator is often called a multiplicative
-congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c ≠ 0, the
+congruential generator (MCG), or Lehmer RNG (which is used for our implementation). If c $\neq$ 0, the
 method is called a mixed congruential generator.
@@
 $\mathbb{Y}_n$ represents a set containing $n$ sets of $k$th values with a direct mapping to each $\mathbb{X}_n$ such that $\mathbb{X}_n \mapsto \mathbb{Y}_n$.
-$P$ a predictor function that represents a convolutional neural network, which takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on back-propagation due to previous predictions, thus using supervised learning to build a regression model.
+$P$ is a predictor function that represents a convolutional neural network, which takes in $\mathbb{X}_n$ and $\mathbb{Y}_n$, yields a new set $\mathbb{B}_n$ implied from $\mathbb{X}_n$, where the model trains $\mathbb{B}_n$ to be similar or equal to $\mathbb{Y}_n$ based on back-propagation due to previous predictions, thus using supervised learning to build a regression model.
 
@@
 Some generators have tight tolerances for parameters and algorithmic behaviors.
-While we believe that our implementations are sound, they could be checked and improved upon by using tests of statistical randomnesses, such as the National Institute of Standards and Technology (NIST) provides.
+While we believe that our implementations are sound, they could be checked and improved upon by using tests of statistical randomnesses, like the National Institute of Standards and Technology (NIST) provides.
 Different seeding methods could also provide different results, given that our seeding method was relatively linear and weak in design.

### 2020-05-03 WorkSpace/Paper/Paper.tex
fixed paper

@@
 \begin{itemize}
-    \item "In 1988, Park and Miller \cite{10.1145/63039.63042}, suggested a Lehmer RNG with particular parameters m = 231 − 1 = 2,147,483,647 (a Mersenne prime M31) and a = 75 = 16,807 (a primitive root modulo M31), now known as MINSTD." \cite{ParkMiller}
+    \item "In 1988, Park and Miller \cite{10.1145/63039.63042}, suggested a Lehmer RNG with particular parameters $m = 2^{31}-1 = 2,147,483,647$ (a Mersenne prime M31) and $a = 7^{5} = 16,807$ (a primitive root modulo M31), now known as MINSTD." \cite{ParkMiller}
 \end{itemize}
